---
title: "workshop2"
author: "Sathwika"
date: "2024-04-06"
output: 
  github_document:
    toc: true
    toc_depth: 2
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Statistics on stock returns

```{r}
wk2_stocks <- readRDS("wk2_stocks.rds")
df = wk2_stocks
mean(df$SPY_returns)
sd(df$SPY_returns)
```

+ The cumulative returns of the S&P index during this period is `r round(sum(df$SPY_returns)*100,2)`%.
+ The average daily returns of the S&P index during this period is `r round(mean(df$SPY_returns)*100,2)`%.
+ The standard deviation of the daily returns of the S&P index during this period is `r round(sd(df$SPY_returns)*100,2)`%.


## Plot 1

```{r}
library(tidyverse)
ggplot(df,aes(x = date, y =SPY_prices))+
  geom_line()

```

## Plot 2

```{r}
df%>%
  mutate(year = year(date))%>%
  filter(year <= 2023)%>%
  group_by(year)%>%
  summarise(returns = sum(SPY_returns)) %>%
ggplot(aes(x = year, y = returns))+
  geom_col()

```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
